Luminance constancy under fixed geometry

### 2018-01-28 Draft2/draft2.tex
todays work

%% Figure Results
\begin{figure}
\centering
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingIsomerizationTargetColor.pdf}
        \caption{Target color variation}
        \label{fig:renderingIsomerizationTargetColor}
    \end{subfigure}    
%    \begin{subfigure}[b]{0.33 \textwidth}   
 %       \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
%        \caption{Rendering noise}
%        \label{fig:renderingNoise}
%    \end{subfigure}
            \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
        \caption{Luminance Estimates}
        \label{fig:case9Results}
    \end{subfigure}    
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingAndIsomerization.pdf}
        \caption{Rendering and isomerization noise}
        \label{fig:renderingAndIsomerization}
    \end{subfigure}
    \caption{Different sources of noise}
\label{fig:sourcesOfNoise}
\end{figure}

@@

%% Figure 9
\begin{figure}
\centering
    \begin{subfigure}[b]{0.4 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case9AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.27 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
        \caption{AMA RF Response}
        \label{fig:case9FiltersResponse}
    \end{subfigure}
    \caption{{\bf Receptive fields and luminance estimates. Case 1:} (a) First two receptive fields produced by the AMA. Along the row we show the filters corresponding to the L cones, M cones and S cones (left to right). (b) The response of the stimuli to the first two AMA filters. The responses are grouped with the label of the stimuli. As is clear, the response distributions at each luminance level separate out well in this case, resulting in good estimates of the target object luminance. (c) The estimates of the target object standard luminance. The naive method produces the mean value of the target luminance used in the analysis. The shaded region corresponds to 1 sigma standard deviation.}
\label{fig:case9AllResults}
\end{figure}

%% Figure Isomerization Fails
\begin{figure}
\centering
    \begin{subfigure}[b]{0.3	 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/isomerizationFails.pdf}
        \caption{AMA on isomerization fails in case of variation in illuminant}
        \label{fig:isomerizationFails}
    \end{subfigure}
    ~
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/constrastWorks.pdf}
        \caption{Converting signal to contrast solves the problem}
        \label{fig:constrastWorks}
    \end{subfigure}
    \caption{Need for contrast conversion.}
\label{fig:importanceOfConstrast}
\end{figure}

>>>>

%% Figure Results
\begin{figure}
\centering
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
        \caption{Target color variation}
        \label{fig:renderingIsomerizationTargetColor}
    \end{subfigure}    
%    \begin{subfigure}[b]{0.33 \textwidth}   
 %       \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
%        \caption{Rendering noise}
%        \label{fig:renderingNoise}
%    \end{subfigure}
            \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
        \caption{Luminance Estimates}
        \label{fig:case9Results}
    \end{subfigure}    
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
        \caption{Rendering and isomerization noise}
        \label{fig:renderingAndIsomerization}
    \end{subfigure}
    \caption{Different sources of noise}
\label{fig:sourcesOfNoise}
\end{figure}

@@

%% Figure Isomerization Fails
\begin{figure}
\centering
    \begin{subfigure}[b]{0.3	 \textwidth}   
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/isomerizationFails.pdf}
        \caption{AMA on isomerization fails in case of variation in illuminant}
        \label{fig:isomerizationFails}
    \end{subfigure}
    ~
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/resultsFigure/contrastWorks.pdf}
        \caption{Converting signal to contrast solves the problem}
        \label{fig:constrastWorks}
    \end{subfigure}
            \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.pdf}
        \caption{Luminance Estimates}
        \label{fig:case10Results}
    \end{subfigure}
    \caption{Need for contrast conversion.}
\label{fig:importanceOfConstrast}
\end{figure}
